---
title: "Pushup Problem"
author: "Jose Guzman"
date: "09/18/2019"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}

require(tidyverse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

Create an Rstudio project called pushups in your project folders directory. Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups that can be done in two minutes between line vs skill players

$H_A$: The average number of pushups that can be done in two minutes is statistically different for skilled and line players.



```{r}
players <- pushups
```
Two football players at GC asked their team-mates to do as many pushups as they could in two minutes.

Format

A data frame with 30 observations on the following 3 variables.

**weight**
weight of subject in pounds.

**pushups**
number of pushups completed.

**position**
a factor with levels LINE SKILL: type of position played by the subject. Line positions require high body mass, skill positions require a lot of running around.  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
  
Our variable analysis gives weight and pushups as numerical variables and position as a factor variable.  The two variables of interest are weight and position. Graphical displays would include boxplots as a first thing to look at.
#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
 We typically look at boxplots when considering numerical vs categorical data.  below is our boxplot.

```{r}
boxplot(pushups~position,data=players,main="Pushups done in 2 minutes")
```
  
Based on the information on the boxplot; the skilled players have a higher median of pushups than the pushups done by the line players. 
 
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
summary(pushups)
```
This table shows the minimum median, mean done in two minutes for all members of the team. 




## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

The test we will use is the t-test.

```{r}
t.test(pushups~position,data=players)
```
Based on this T-test, the average number of pusups done within the line position is roughly 17, with the average number of pushups for the skill players is roughly 50.
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The question was, "is there a difference in the numer of pushups done in 2 minutes of players in the line and skill postion?

The null hypothesis is $H_0$  is, "there is no difference between the average number of pushups done of players in the line or skill postions"

Since the P value is less than 0.05 We reject the null hypothesis and conclude that there is a difference in the average number of pushups that can be done in two minutes. 